Supplemental Online Materials:\\\textit{Double Standards in Judging Collective Action}

### 2022-09-19 Documents/manuscript.Rmd
update preprint

---
title: "Double Standards in Judging Collective Action"
header: "DOUBLE STANDARDS"
keywords: protest, collective action, double standards, social identity theory, system justification theory, Black Lives Matter
abstract: "Collective action is a powerful force driving social change but often sparks contention about what actions are acceptable means to effect social change. In five studies (total *N* = 2,979), we investigated double standards in judging collective action---that is, whether observers will judge the same protest actions as more acceptable if the protesters are ingroup members and their cause aligns with the ingroup's interests (*identity-based double standards*) or if the protesters' cause aligns with the observers' ideological positions (*ideology-based double standards*). In two studies, we developed an instrument of 25 controversial protest actions, based in item response theory, to measure where people draw the line between acceptable and unacceptable forms of collective action. In three preregistered experiments, we used this instrument to test for double standards in judging collective action for workers' rights in the United Kingdom and for or against defunding the police and for or against restricting abortion in the United States. We found evidence for ideology-based, but not for identity-based, double standards: Participants judged the same protest actions to be more acceptable when the protesters' cause aligned with their own ideological position---but showed no consistent ingroup bias when judging collective action by ingroup and outgroup members. Our findings have theoretical and practical implications for understanding the often divided response to prominent social movements."
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: yes
    template: preprint-template.tex

@@

Recent research has shown that this distinction matters for how people respond to collective action. @shuman_disrupting_2021 showed that non-normative, non-violent collective action is more effective than either normative or violent collective action at gaining concessions from those most resistant to social change. @feinberg_activists_2020 demonstrated, however, that observers are less supportive of social movements that use extreme protest actions. Similarly, @teixeira_is_2020 found that advantaged-group members perceive non-normative collective action by disadvantaged-group members as more damaging to their ingroup's social image and are thus less supportive of such action. @verkuyten_intolerance_2022 found that, in general, the public tends to be intolerant of non-normative collective action. This means that activists face the dilemma that non-normative collective action might be most effective at gaining concessions but that it also risks reducing popular support for a cause. Together, these studies show that the distinction between normative and non-normative collective action is psychologically and societally consequential.

@@

<!-- That is, we hypothesize that, at least to the extent that they hold system-justifying beliefs, people will judge the same protest actions as more acceptable if the protest supports, rather than challenges, the system. -->

@@

>>>>

---
title: "Double Standards in Judging Collective Action"
header: "DOUBLE STANDARDS"
keywords: protest, collective action, double standards, social identity theory, system justification theory, Black Lives Matter
abstract: "Collective action is a powerful force driving social change but often sparks contention about what actions are acceptable means to effect social change. In five studies (total *N* = 2,979), we investigated double standards in judging collective action---that is, whether observers will judge the same protest actions as more acceptable if the protesters are ingroup members and their cause aligns with the ingroup's interests (*identity-based double standards*) or if the protesters' cause aligns with the observers' ideological positions (*ideology-based double standards*). In two studies, we developed an instrument of 25 controversial protest actions, based in item response theory, to measure where people draw the line between acceptable and unacceptable forms of collective action. In three preregistered experiments, we used this instrument to test for double standards in judging collective action for workers' rights in the United Kingdom and for or against defunding the police and for or against restricting abortion in the United States. We found evidence for ideology-based, but not for identity-based, double standards: Participants judged the same protest actions to be more acceptable when the protesters' cause aligned with their own ideological position---but showed no consistent ingroup bias when judging collective action by ingroup and outgroup members. Our findings have theoretical and practical implications for understanding the often divided response to prominent social movements."
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: yes
    template: apa-template.tex

@@

Recent research has shown that this distinction matters for how people respond to collective action. @shuman_disrupting_2021 showed that non-normative, non-violent collective action is more effective than either normative or violent collective action at gaining concessions from those most resistant to social change. @feinberg_activists_2020 demonstrated, however, that observers are less supportive of social movements that use extreme protest actions.^[In contrast, White Americans exposed to pictures of destructive Black Lives Matter protests were not, on average, any less supportive of systemic change than those exposed to pictures of peaceful protests [@teixeira_white_2022].] Similarly, @teixeira_is_2020 found that advantaged-group members perceive non-normative collective action by disadvantaged-group members as more damaging to their ingroup's social image and are thus less supportive of such action. @verkuyten_intolerance_2022 found that, in general, the public tends to be intolerant of non-normative collective action. This means that activists face the dilemma that non-normative collective action might be most effective at gaining concessions but that it also risks reducing popular support for a cause. Together, these studies show that the distinction between normative and non-normative collective action is psychologically and societally consequential.

@@

@@

Our findings provided a relevant comparison to findings from a recent experiment in which White Americans viewed pictures of either peaceful or destructive Black Lives Matter protests and rated how legitimate (i.e., fair, reasonable, legitimate, and justified) they considered the pictured protests to be [@teixeira_white_2022]. In this experiment, more conservative participants rated destructive and, to a lesser extent, peaceful protests to be less legitimate than more liberal participants. Likewise, participants who identified more strongly with their ethnic ingroup rated destructive and, to a lesser extent, peaceful protests to be less legitimate than participants who identified less strongly with their ingroup. However, participants' group identification was no longer associated with their protest ratings after controlling for their political orientation.^[These findings are based on our reanalysis, reported in the SOM, of Teixeira et al.'s [-@teixeira_white_2022] experiment. We thank the authors for making their data available online.] In this way, results from the experiment aligned with our conclusion that political ideologies are more important than social identities for shaping how people judge controversial forms of collective action.

### 2022-09-19 Documents/manuscript.tex
update preprint

\documentclass[12pt, letterpaper]{article}

% Font
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{microtype}

% Format
\usepackage[letterpaper, margin = 1in]{geometry}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0.5in}
\usepackage[compact]{titlesec}
\titleformat*{\section}{\centering\normalfont\normalsize\bfseries}
\titleformat*{\subsection}{\raggedright\normalfont\normalsize\bfseries}
\titleformat*{\subsubsection}{\raggedright\normalfont\normalsize\bfseries\itshape}
\newcommand{\refsection}{\newpage \section{References}}
\usepackage{indentfirst}
\usepackage[hang,flushmargin]{footmisc}
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{14.5pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{DOUBLE STANDARDS}
\fancyhead[R]{\thepage}

@@

% Line spacing
\usepackage[doublespacing]{setspace}

% Frontmatter
\title{ Double Standards in Judging Collective Action }

@@

\section{Abstract}

\noindent Collective action is a powerful force driving social change
but often sparks contention about what actions are acceptable means to
effect social change. In five studies (total \emph{N} = 2,979), we
investigated double standards in judging collective action---that is,
whether observers will judge the same protest actions as more acceptable
if the protesters are ingroup members and their cause aligns with the
ingroup's interests (\emph{identity-based double standards}) or if the
protesters' cause aligns with the observers' ideological positions
(\emph{ideology-based double standards}). In two studies, we developed
an instrument of 25 controversial protest actions, based in item
response theory, to measure where people draw the line between
acceptable and unacceptable forms of collective action. In three
preregistered experiments, we used this instrument to test for double
standards in judging collective action for workers' rights in the United
Kingdom and for or against defunding the police and for or against
restricting abortion in the United States. We found evidence for
ideology-based, but not for identity-based, double standards:
Participants judged the same protest actions to be more acceptable when
the protesters' cause aligned with their own ideological position---but
showed no consistent ingroup bias when judging collective action by
ingroup and outgroup members. Our findings have theoretical and
practical implications for understanding the often divided response to
prominent social movements.

\textit{Keywords:} protest, collective action, double standards, social
identity theory, system justification theory, Black Lives Matter

\section{Double Standards in Judging Collective Action}

Protest movements often spark contention about what actions are
acceptable means of protest. Reactions to Black American athletes
kneeling during the national anthem to protest racist police violence
are a case in point. Kneeling during the national anthem is not violent,
disruptive, or illegal. And yet, only 29\% of White Americans (compared
to 66\% of Black Americans) and 11\% of Republicans (compared to 59\% of
Democrats) considered it appropriate for Black athletes to protest in
this way (YouGov, 2017). Indeed, Black athletes who had participated in
the protests faced a backlash in public opinion (Lacina, 2020). This and
other examples suggest that \emph{who} the protesters are and
\emph{what} they are protesting influences how acceptable observers
judge their actions to be.

@@

Recent research has shown that this distinction matters for how people
respond to collective action. Shuman et al. (2021) showed that
non-normative, non-violent collective action is more effective than
either normative or violent collective action at gaining concessions
from those most resistant to social change. Feinberg et al. (2020)
demonstrated, however, that observers are less supportive of social
movements that use extreme protest actions. Similarly, Teixeira et al.
(2020) found that advantaged-group members perceive non-normative
collective action by disadvantaged-group members as more damaging to
their ingroup's social image and are thus less supportive of such
action. Verkuyten et al. (2022) found that, in general, the public tends
to be intolerant of non-normative collective action. This means that
activists face the dilemma that non-normative collective action might be
most effective at gaining concessions but that it also risks reducing
popular support for a cause. Together, these studies show that the
distinction between normative and non-normative collective action is
psychologically and societally consequential.

@@

@@

>>>>

\documentclass[twocolumn, 11pt, letterpaper]{article}

% Font
\usepackage[utf8]{inputenc}
\usepackage{MinionPro} 
\input{glyphtounicode}
\pdfgentounicode=1 
\usepackage{microtype}

% Format
\usepackage[letterpaper, margin = 1in]{geometry}
\setlength{\columnsep}{18pt}
\setcounter{secnumdepth}{0}
\usepackage[compact]{titlesec}
\titleformat*{\section}{\centering\normalfont\Large\bfseries}
\titleformat*{\subsection}{\raggedright\normalfont\normalsize\bfseries}
\titleformat*{\subsubsection}{\raggedright\normalfont\normalsize\bfseries\itshape}
\usepackage{authblk}
\renewcommand\Affilfont{\small}
\newcommand{\refsection}{\section{References}}
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

% Frontmatter
\title{ Double Standards in Judging Collective Action\thanks{} }
\author[1]{Nils K. Reimer}
\affil[1]{University of California, Santa Barbara, United States}
\author[2]{Marija Brankovi\'{c}}
\affil[2]{Singidunum University and University of Belgrade, Serbia}
\author[3]{Iniobong Essien}
\affil[3]{Leuphana University of L\"{u}neburg, Germany}
\author[4]{Jin X. Goh}
\affil[4]{Colby College, United States}
\author[5]{S\'{e}bastien Goudeau}
\affil[5]{University of Poitiers, France}
\author[6]{N\'{o}ra A. Lantos}
\affil[6]{E\"{o}tv\"{o}s Lor\'{o}nd University, Hungary}
\author[7]{Jenny Veldman}
\affil[7]{NYU Abu Dhabi, United Arab Emirates}

@@

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      \noindent Collective action is a powerful force driving social
change but often sparks contention about what actions are acceptable
means to effect social change. In five studies (total \emph{N} = 2,979),
we investigated double standards in judging collective action---that is,
whether observers will judge the same protest actions as more acceptable
if the protesters are ingroup members and their cause aligns with the
ingroup's interests (\emph{identity-based double standards}) or if the
protesters' cause aligns with the observers' ideological positions
(\emph{ideology-based double standards}). In two studies, we developed
an instrument of 25 controversial protest actions, based in item
response theory, to measure where people draw the line between
acceptable and unacceptable forms of collective action. In three
preregistered experiments, we used this instrument to test for double
standards in judging collective action for workers' rights in the United
Kingdom and for or against defunding the police and for or against
restricting abortion in the United States. We found evidence for
ideology-based, but not for identity-based, double standards:
Participants judged the same protest actions to be more acceptable when
the protesters' cause aligned with their own ideological position---but
showed no consistent ingroup bias when judging collective action by
ingroup and outgroup members. Our findings have theoretical and
practical implications for understanding the often divided response to
prominent social movements.
    \end{abstract}
  \end{@twocolumnfalse}
  % \renewcommand{\abstractname}{Statement of Relevance}
  % \begin{@twocolumnfalse}
  %   \maketitle
  %   \begin{abstract}
  %   \noindent 
  %   \end{abstract}
  % \end{@twocolumnfalse}
]

{
  \renewcommand{\thefootnote}%
    {\fnsymbol{footnote}}
  \footnotetext[1]{M.B.--J.V. are listed in alphabetical order. This research was supported by a Seedcorn Research Grant from the European Association of Social Psychology.}
}

\noindent Protest movements often spark contention about what actions
are acceptable means of protest. Reactions to Black American athletes
kneeling during the national anthem to protest racist police violence
are a case in point. Kneeling during the national anthem is not violent,
disruptive, or illegal. And yet, only 29\% of White Americans (compared
to 66\% of Black Americans) and 11\% of Republicans (compared to 59\% of
Democrats) considered it appropriate for Black athletes to protest in
this way (YouGov, 2017). Indeed, Black athletes who had participated in
the protests faced a backlash in public opinion (Lacina, 2020). This and
other examples suggest that \emph{who} the protesters are and
\emph{what} they are protesting influences how acceptable observers
judge their actions to be.

@@

Recent research has shown that this distinction matters for how people
respond to collective action. Shuman et al. (2021) showed that
non-normative, non-violent collective action is more effective than
either normative or violent collective action at gaining concessions
from those most resistant to social change. Feinberg et al. (2020)
demonstrated, however, that observers are less supportive of social
movements that use extreme protest actions.\footnote{In contrast, White
  Americans exposed to pictures of destructive Black Lives Matter
  protests were not, on average, any less supportive of systemic change
  than those exposed to pictures of peaceful protests (Teixeira et al.,
  2022).} Similarly, Teixeira et al. (2020) found that advantaged-group
members perceive non-normative collective action by disadvantaged-group
members as more damaging to their ingroup's social image and are thus
less supportive of such action. Verkuyten et al. (2022) found that, in
general, the public tends to be intolerant of non-normative collective
action. This means that activists face the dilemma that non-normative
collective action might be most effective at gaining concessions but
that it also risks reducing popular support for a cause. Together, these
studies show that the distinction between normative and non-normative
collective action is psychologically and societally consequential.

@@

Our findings provided a relevant comparison to findings from a recent
experiment in which White Americans viewed pictures of either peaceful
or destructive Black Lives Matter protests and rated how legitimate
(i.e., fair, reasonable, legitimate, and justified) they considered the
pictured protests to be (Teixeira et al., 2022). In this experiment,
more conservative participants rated destructive and, to a lesser
extent, peaceful protests to be less legitimate than more liberal
participants. Likewise, participants who identified more strongly with
their ethnic ingroup rated destructive and, to a lesser extent, peaceful
protests to be less legitimate than participants who identified less
strongly with their ingroup. However, participants' group identification
was no longer associated with their protest ratings after controlling
for their political orientation.\footnote{These findings are based on
  our reanalysis, reported in the SOM, of Teixeira et al.'s (2022)
  experiment. We thank the authors for making their data available
  online.} In this way, results from the experiment aligned with our
conclusion that political ideologies are more important than social
identities for shaping how people judge controversial forms of
collective action.

@@

\leavevmode\vadjust pre{\hypertarget{ref-teixeira_white_2022}{}}%
Teixeira, C. P., Leach, C. W., \& Spears, R. (2022). White {Americans}'
belief in systemic racial injustice and in-group identification affect
reactions to ({peaceful} vs. {destructive}) {``{Black Lives Matter}''}
protest. \emph{Psychology of Violence}, \emph{12}(4), 280--292.
\url{https://doi.org/10.1037/vio0000425}

### 2022-09-19 Documents/supplemental-materials.Rmd
update preprint

>>>>

# Reanalysis of Teixeira et al.'s [-@teixeira_white_2022] experiment

At the height of the 2020 Black Lives Matter protests, @teixeira_white_2022 exposed White Americans ($N = 399$) to photos of either peaceful or destructive Black Lives Matter protests and asked them to rate how legitimate (i.e., fair, reasonable, legitimate, and justified) they thought the pictured protests were. As such, their findings make for an interesting comparison to our findings. @teixeira_white_2022, however, reported results from a linear model estimating the three-way interaction between the experimental manipulation, belief in systemic racial injustice, and group identification while controlling for political orientation. This analysis did not provide a direct comparison to our findings.

To compare theirs to our findings, we instead estimated a series of simpler linear regression models, using the brms R package [@burkner_brms_2017; @burkner_advanced_2018] and weakly informative Student-*t* $(3, 0, 2.5)$ prior distributions, with participants' ratings of how legitimate the pictured protests were as the outcome variable.^[We thank the authors for making their data available online ([https://osf.io/sud2y/](https://osf.io/sud2y/)).] First, we found that, as expected, participants considered peaceful protests far more legitimate than destructive protests ($\text{Cohen's}~d = 1.14, [0.98, 1.30]$). Second, we found that more conservative participants rated destructive protests ($\beta_{xy} = -0.59, [-0.68, -0.49]$) and, to a lesser extent, peaceful protests ($\beta_{xy} = -0.20, [-0.30, -0.10]$) to be less legitimate than more liberal participants. Third, we found that participants who identified more strongly with their (White American) ethnic identity rated destructive protests ($\beta_{xy} = -0.35, [-0.45, -0.24]$) and, to a lesser extent, peaceful protests ($\beta_{xy} = -0.10, [-0.21, 0.01]$) to be less legitimate than participants who identified less strongly with their (White American) ethnic identity. Finally, we found that participants' group identification was no longer associated with how legitimate they rated peaceful ($\beta_{xy} = -0.02, [-0.13, 0.05]$) and destructive ($\beta_{xy} = -0.06, [-0.17, 0.05]$) protests to be after controlling for their political orientation. We refer to findings from our reanalysis of Teixeira et al.'s [-@teixeira_white_2022] experiment in the main text.

### 2022-09-19 Documents/supplemental-materials.tex
update preprint

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-betancourt_ordinal_2019}{}}%
Betancourt, M. (2019). \emph{Ordinal regression}.
\url{https://betanalpha.github.io/assets/case_studies/ordinal_regression.html}

@@

>>>>

\hypertarget{experiment-3}{%
\section{Experiment 3}\label{experiment-3}}

\hypertarget{method-1}{%
\subsection{Method}\label{method-1}}

\hypertarget{measures}{%
\subsubsection{Measures}\label{measures}}

We included additional measures not used in the analyses reported in
this paper.

We included a three-item measure of moral conviction (Ryan, 2014) that
assessed to what extent participants' feelings about restricting or
banning abortion were, for example, connected to their core moral
beliefs or convictions (1 = \emph{not at all}, 5 = \emph{very much}).

We measured gender-related system-justifying beliefs with eight items
(adapted from Jost \& Kay, 2005), for example, ``in general, relations
between men and women are fair'' (1 = \emph{strongly disagree}, 7 =
\emph{strongly agree}; McDonald's \(\omega = .93\)). A confirmatory
factor analysis model in which all items loaded onto a single factor
showed acceptable fit,
\(\chi^2 (20) = 111.90; \text{CFI} = 0.97; \text{TLI} = 0.95; \text{RMSEA} = 0.09, [0.08, 0.11]\).

We measured moral concerns with the 36-item moral foundations
questionnaire (MFQ-2, Atari et al., 2022) which assesses to what extent
participants endorse concerns about care, equality, proportionality,
loyalty, authority, and purity (e.g., ``I believe chastity is an
important virtue.''; 1 = \emph{does not describe me at all}, 5 =
\emph{describes me extremely well}). We embedded three further attention
checks within the questionnaire (e.g., ``To show that you are paying
attention and giving your best effort, please select `moderately
describes me'.'').

\hypertarget{reanalysis-of-teixeira-et-al.s--teixeira_white_2022-experiment}{%
\section{Reanalysis of Teixeira et al.'s (2022)
experiment}\label{reanalysis-of-teixeira-et-al.s--teixeira_white_2022-experiment}}

At the height of the 2020 Black Lives Matter protests, Teixeira et al.
(2022) exposed White Americans (\(N = 399\)) to photos of either
peaceful or destructive Black Lives Matter protests and asked them to
rate how legitimate (i.e., fair, reasonable, legitimate, and justified)
they thought the pictured protests were. As such, their findings make
for an interesting comparison to our findings. Teixeira et al. (2022),
however, reported results from a linear model estimating the three-way
interaction between the experimental manipulation, belief in systemic
racial injustice, and group identification while controlling for
political orientation. This analysis did not provide a direct comparison
to our findings.

To compare theirs to our findings, we instead estimated a series of
simpler linear regression models, using the brms R package (Bürkner,
2017, 2018) and weakly informative Student-\emph{t} \((3, 0, 2.5)\)
prior distributions, with participants' ratings of how legitimate the
pictured protests were as the outcome variable.\footnote{We thank the
  authors for making their data available online
  (\url{https://osf.io/sud2y/}).} First, we found that, as expected,
participants considered peaceful protests far more legitimate than
destructive protests (\(\text{Cohen's}~d = 1.14, [0.98, 1.30]\)).
Second, we found that more conservative participants rated destructive
protests (\(\beta_{xy} = -0.59, [-0.68, -0.49]\)) and, to a lesser
extent, peaceful protests (\(\beta_{xy} = -0.20, [-0.30, -0.10]\)) to be
less legitimate than more liberal participants. Third, we found that
participants who identified more strongly with their (White American)
ethnic identity rated destructive protests
(\(\beta_{xy} = -0.35, [-0.45, -0.24]\)) and, to a lesser extent,
peaceful protests (\(\beta_{xy} = -0.10, [-0.21, 0.01]\)) to be less
legitimate than participants who identified less strongly with their
(White American) ethnic identity. Finally, we found that participants'
group identification was no longer associated with how legitimate they
rated peaceful (\(\beta_{xy} = -0.02, [-0.13, 0.05]\)) and destructive
(\(\beta_{xy} = -0.06, [-0.17, 0.05]\)) protests to be after controlling
for their political orientation. We refer to findings from our
reanalysis of Teixeira et al.'s (2022) experiment in the main text.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-atari_morality_2022}{}}%
Atari, M., Haidt, J., Graham, J., Koleva, S., Stevens, S. T., \&
Dehghani, M. (2022). Morality beyond the {WEIRD}: How the nomological
network of morality varies across cultures. \emph{PsyArXiv}.
\url{https://doi.org/10.31234/osf.io/q6c9r}

\leavevmode\vadjust pre{\hypertarget{ref-betancourt_ordinal_2019}{}}%
Betancourt, M. (2019). \emph{Ordinal regression}.
\url{https://betanalpha.github.io/assets/case_studies/ordinal_regression.html}

\leavevmode\vadjust pre{\hypertarget{ref-burkner_brms_2017}{}}%
Bürkner, P.-C. (2017). {brms}: An {R} package for bayesian multilevel
models using {Stan}. \emph{Journal of Statistical Software},
\emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\leavevmode\vadjust pre{\hypertarget{ref-burkner_advanced_2018}{}}%
Bürkner, P.-C. (2018). Advanced bayesian multilevel modeling with the
{R} package brms. \emph{The R Journal}, \emph{10}(1), 395--411.
\url{https://doi.org/10.32614/RJ-2018-017}

@@

\leavevmode\vadjust pre{\hypertarget{ref-jost_exposure_2005}{}}%
Jost, J. T., \& Kay, A. C. (2005). Exposure to benevolent sexism and
complementary gender stereotypes: Consequences for specific and diffuse
forms of system justification. \emph{Journal of Personality and Social
Psychology}, \emph{88}(3), 498--509.
\url{https://doi.org/10.1037/0022-3514.88.3.498}

\leavevmode\vadjust pre{\hypertarget{ref-ryan_reconsidering_2014}{}}%
Ryan, T. J. (2014). Reconsidering moral issues in politics. \emph{The
Journal of Politics}, \emph{76}(2), 380--397.
\url{https://doi.org/10.1017/S0022381613001357}
